Co-citations in context

### 2019-06-13 cocit_r.tex
Minor revisions

Since the constrained model better fits the observed data, we evaluated the distribution of 
highly cited articles  (i.e., ``hit articles")
 in the four categories (HCHN, LCHN, HCLN, LCLN), for different
thresholds for hit articles.
Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Metabolism, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category. 
The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2})
mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency. 
However, the trends  for all three  disciplinary subnetworks  are different from those for WoS.
Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%),
and the highest hit rates for the 1995 applied physics datasets are in the 
HNLC category for both the top 1\% and top 10\% of all cited articles.  
%Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}). 
 Thus, the category exhibiting the highest hit rate (among highly cited papers) depends on the
specific disciplinary network and to some extent on the threshold for being highly cited.
 %was the case with immunology. 
Furthermore, the categories displaying the greatest hit rate vary 
to some extent % with parameter settings and 
with the year  \textcolor{blue}{(data not shown)}.
%The lack of stable results across parameter settings suggests that parameters must be selected judiciously.

>>>>

Since the constrained model better fits the observed data, we evaluated the distribution of 
highly cited articles  (i.e., ``hit articles")
 in the four categories (HCHN, LCHN, HCLN, LCLN), for different
thresholds for hit articles.
Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Metabolism, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category. 
The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2})
mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency. 
However, the trends  for all three  disciplinary subnetworks  are different from those for WoS.
Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%),
and the highest hit rates for the 1995 applied physics datasets are in the 
HNLC category for both the top 1\% and top 10\% of all cited articles.  
%Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}). 
 Thus, the category exhibiting the highest hit rate \textcolor{blue}{(among highly cited papers)} depends on the
specific disciplinary network and to some extent on the \textcolor{blue}{threshold for being highly cited}.
 %was the case with immunology. 
Furthermore, the categories displaying the greatest hit rate vary 
to some extent % with parameter settings and 
with the year  \textcolor{blue}{(data not shown)}.
%The lack of stable results across parameter settings suggests that parameters must be selected judiciously.
